### 2020-01-28 2020/WCGO_MCO_OptimizationLetters/2020_WCGO_MCO.tex
Fix misprints suggested by Harley

To reduce the complexity of solving optimization problems with constraints, simpler cases are often highlighted; for example, problems with linear or quadratic constraints are selected. Various methods of approximating complex constraints with the aid of simpler forms (linear, convex, etc.) are widely used. However, the penalty function method is most commonly used, when calculating in an unfeasble region $\Delta \setminus \Delta_g$, some ``penalty'' are added to the values of the minimized function. But the penalty function method often involves repeatedly solving the optimization problem to determine a sufficient value of the penalty coefficient. More complete information on methods for solving optimization problems with constraints can be obtained, for example, in monographs \cite{c18,c26,c27}.

@@

We apply a sequential scheme to obtain the constraint values $g_i(y(x)) \leq 0$, $1 \leq i \leq m$, and the minimized function $\varphi(x)$, according to which the constraint values are calculated strictly in the order of their numbers, and the calculations immediately stop when the first violated constraint is detected (the partial computability scheme). The number of constraints in which the values were calculated will be referred below as the index $\nu=\nu(x)$, that is
\begin{equation}\label{eq:15}
\nu(x) : g_\nu(x)>0, g_j(x)\leq 0, 1 \leq j\leq \nu - 1, 1\leq \nu = \nu(x) \leq m
\end{equation}
 (when all the constraints are satisfied, $\nu=m+1$ is assumed). Introducing the index concept allows us to determine the integrated function for the problem (\ref{eq:13}) (see Fig. \ref{fig:1})
\begin{equation}\label{eq:16}
F(x)=g_\nu(x), \nu=\nu(x),
\end{equation}
defined and computable everywhere in $[0,1]$. Its value at the point $x\in [0,1]$ is either the value of the left side of the constraint violated at this point (the case when $\nu \leq m$), or the value of the minimized function (the case when $\nu = m + 1$). The process of calculating the value of $F(x)$, $x\in [0,1]$, is completed either as a result of establishing the inequality $g_j(x)>0$, or as a result of reaching the value $\nu(x)=m+1$ (below, this procedure is called a \textit{trial}).

@@

Moreover, using search information $A_k$ allows to reduce the multistage solution of the MCO problem in accordance with the scheme (\ref{eq:7}) to the solution of the only global optimization problem in the last stage of the scheme (\ref{eq:7}), namely 
\begin{equation}\label{eq:26}
P_{\delta lex} (f,\delta,D)=Arg \min_{y\in D}{f_s(y)}, f_j(y)\leq f_j^*+\delta_j, 1 \leq j < s,
\end{equation}
where for the unknown a priori values $f_j^*$, $1 \leq j < s$, can be used the estimates $z_j^k$, $1 \leq j < s$, from (\ref{eq:20}) obtained from the search information $A_k$,  and for the constants $\delta_j$, $1 \leq j<s$, we can use the values normalized to the range of constraints values, that is
\begin{equation}\label{eq:27}
	\begin{matrix}
	\delta_j=z_j^k+\theta_j (g_j^k-z_j^k ),\; 0\leq \theta_j\leq 1, \; 1 \leq j < s,\\
	g_j^k= \max{\{ g_j (x_i ) : \nu(x_i)=j,\; 1\leq i\leq k \}}.
	\end{matrix}
\end{equation}

@@

The results from the executed experiments demonstrate that the MAGCS algorithm has a significant advantage in comparison with the considered multicriteria optimization methods of, even when solving relatively simple MCO problems.

@@

In the computational experiments, calculations are terminated when the required accuracy was achieved. When the process was terminated, the solution was evaluated for correctness. As a means of control, we compared the solution points found by MAGCS and the points calculated from the Pareto boundary, taking into account the selected values of $\theta_j$, $1 \leq j < s$. The method parameters were set as foolows: the accuracy $\varepsilon = 0.02$ and the reliability $r_1=r_2=5.6$. Results of the computational experiments are presented in Table 2.

@@

In the third series of computational experiments, the two-criteria four-dimensional MCO problems were solved. As in the second series of computational experiments, 100 multicriteria problems were solved. In each problem, the Pareto-optimal decisions were calculated for 50 different values of $\theta_j$, $1 \leq j <s$, uniformly distributed in the interval $[0,1]$. The criteria of the MCO problems being solved were determined using the GKLS generator \cite{c37}. The method parameters were set as foolows: the accuracy $\varepsilon = 0.025$ and the reliability $r_1=r_2=5.6$. The results of computational experiments are presented in Table 3.

>>>>

To reduce the complexity of solving optimization problems with constraints, simpler cases are often highlighted; for example, problems with linear or quadratic constraints are selected. Various methods of approximating complex constraints with the aid of simpler forms (linear, convex, etc.) are widely used. However, the penalty function method is most commonly used, when calculating in an unfeasible region $\Delta \setminus \Delta_g$, some ``penalty'' is added to the values of the minimized function. But the penalty function method often involves repeatedly solving the optimization problem to determine a sufficient value of the penalty coefficient. More complete information on methods for solving optimization problems with constraints can be obtained, for example, in monographs \cite{c18,c26,c27}.

@@

We apply a sequential scheme to obtain the constraint values $g_i(y(x)) \leq 0$, $1 \leq i \leq m$, and the minimized function $\varphi(x)$, according to which the constraint values are calculated strictly in the order of their numbers, and the calculations immediately stop when the first violated constraint is detected (the partial computability scheme). The number of constraints in which the values were calculated will be indicated below as the index $\nu=\nu(x)$, that is
\begin{equation}\label{eq:15}
\nu(x) : g_\nu(x)>0, g_j(x)\leq 0, 1 \leq j\leq \nu - 1, 1\leq \nu = \nu(x) \leq m
\end{equation}
 (when all the constraints are satisfied, $\nu=m+1$ is assumed). Introducing the index concept allows us to determine the integrated function for the problem (\ref{eq:13}) (see Fig. \ref{fig:1})
\begin{equation}\label{eq:16}
F(x)=g_\nu(x), \nu=\nu(x),
\end{equation}
defined and computable everywhere in $[0,1]$. Its value at the point $x\in [0,1]$ is either the value of the left side of the constraint violated at this point (the case when $\nu \leq m$), or the value of the minimized function (the case when $\nu = m + 1$). The process of calculating the value of $F(x)$, $x\in [0,1]$, is completed either as a result of establishing the inequality $g_j(x)>0$, or as a result of reaching the value $\nu(x)=m+1$ (below, this procedure is called a \textit{trial}).

@@

Moreover, using search information $A_k$ allows to reduce the multistage solution of the MCO problem in accordance with the scheme (\ref{eq:7}) to the solution of the only global optimization problem in the last stage of the scheme (\ref{eq:7}), namely 
\begin{equation}\label{eq:26}
P_{\delta lex} (f,\delta,D)=Arg \min_{y\in D}{f_s(y)}, f_j(y)\leq f_j^*+\delta_j, 1 \leq j < s,
\end{equation}
where for the unknown a priori values $f_j^*$, $1 \leq j < s$, can be used the estimates $z_j^k$, $1 \leq j < s$, from (\ref{eq:20}) obtained from the search information $A_k$,  and for the constants $\delta_j$, $1 \leq j<s$, we can use the values normalized to the range of the constraints' values, that is
\begin{equation}\label{eq:27}
	\begin{matrix}
	\delta_j=z_j^k+\theta_j (g_j^k-z_j^k ),\; 0\leq \theta_j\leq 1, \; 1 \leq j < s,\\
	g_j^k= \max{\{ g_j (x_i ) : \nu(x_i)=j,\; 1\leq i\leq k \}}.
	\end{matrix}
\end{equation}

@@

The results from the executed experiments demonstrate that the MAGCS algorithm has a significant advantage in comparison with the considered multicriteria optimization methods, even when solving relatively simple MCO problems.

@@

In the computational experiments, calculations are terminated when the required accuracy was achieved. When the process was terminated, the solution was evaluated for correctness. As a means of control, we compared the solution points found by MAGCS and the points calculated from the Pareto boundary, taking into account the selected values of $\theta_j$, $1 \leq j < s$. The method parameters were set as follows: the accuracy $\varepsilon = 0.02$ and the reliability $r_1=r_2=5.6$. Results of the computational experiments are presented in Table 2.

@@

In the third series of computational experiments, the two-criteria four-dimensional MCO problems were solved. As in the second series of computational experiments, 100 multicriteria problems were solved. In each problem, the Pareto-optimal decisions were calculated for 50 different values of $\theta_j$, $1 \leq j <s$, uniformly distributed in the interval $[0,1]$. The criteria of the MCO problems being solved were determined using the GKLS generator \cite{c37}. The method parameters were set as follows: the accuracy $\varepsilon = 0.025$ and the reliability $r_1=r_2=5.6$. The results of computational experiments are presented in Table 3.
